---
title: "BIFS-613 AE2 Part I: RMarkdown"
author: "First Last"
date: "09/01/2019"
output:
  html_document: default
---

## Setup

### Code Chunk 1: Load packages

```{r setup, include=FALSE}
### We use the code chunk option "include=FALSE" because we don't need to print this information

### Global knitr options
knitr::opts_chunk$set(echo = TRUE)

### Load packages/libraries that we will need
library(tidyverse)
```

### Code Chunk 2: Load data

```{r}
exprs <- read_csv("TP53_exprs.csv")
```

## A. TP53 expression by cancer type/tissue

### Code Chunk 3: This is a bad barplot

```{r}
### Using geom_col
ggplot(exprs, aes(x = tissue, y = exprs)) +
  geom_col()

### Alternative, using geom_bar
ggplot(exprs, aes(x = tissue, y = exprs)) +
  geom_bar(stat = "identity")
```

### Code Chunk 4: Plot instead as a boxplot

```{r}
### Enter code in here
```

### Code Chunk 5: Add individual data points

```{r}
### Enter code in here

```

### Code Chunk 6:"Jitter" the points

```{r}
### Enter code in here

```

### Code Chunk 7: Remove outlier points from boxplot

```{r}
### Enter code in here

```

### Code Chunk 8: Color points by sex

```{r}
### Enter code in here

```

### Code Chunk 9: Use custom colors

(female = red; male = blue)

```{r}
### Enter code in here

```

### Code Chunk 10: Add theme

(see: https://ggplot2.tidyverse.org/reference/ggtheme.html)

```{r}
### Enter code in here

```

### Code Chunk 11: Angle x-axis labels (tissue types)

```{r}
### Enter code in here

```

### Code Chunk 12: Plot title

```{r}
### Enter code in here

```

### Code Chunk 13: Save the plot

```{r}
### Enter code in here

```

## B. TP53 expression by age

### Code Chunk 14: Exprs vs. Age

```{r}
### Enter code in here

```

### Code Chunk 15: Linear regression

```{r}
### Enter code in here

```

### Code Chunk 16: By sex

```{r}
### Enter code in here

```

### Code Chunk 17: Additional formatting

Use theme and female/male colors used for previous plot above (p53_exprs_tissue.png), and add a title.

```{r}
### Enter code in here

```

### Code Chunk 18: Save the plot

```{r}
### Enter code in here

```

## Session info

### Code Chunk 19

```{r}
sessionInfo()
```
